Exploiting the Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-25 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
More on Leader Board

% Anuncements
At the start of each of the experiments, a call to participation was promoted through social networks
particularly on Facebook and Twitter social networks.
Is important to note that participants needed to log-in to facebook and give permissions to the application
in order to participate, there were no anonymous volunteers. This permited the automatic access to
each participant's social network and to store a local copy of those friends also participating.

@@

Before launch, each deployment was first tried with a few beta testers. When applying the gammification
technique for the first time a problem was found in this beta stage. Some users were chating by 
giving a rating to an animation even before it was returned from the server, this was done by just
constantly pressing the mouse button. This is a common problem found in systmes appling leader boards.
By making the rewards for tasks achievements visible to other players or providing leader boards are ways of 
encouraging players to compete \cite{hickman2010total}. Because the  problematic consequences of competition, 
which can result in negative conduct, low cooperation and collaboration, or disadvantaging certain player
demographics such as women \cite{kumar2013gamification}, best-practice gamification designs try to
refrain from using this element. In order to measure the effect of the leader board in the system, the 
problem of cheating was mitigated by disabling the buttons for a certain amount of time. But the problem 
persists, competitive users will try to get in to the leader board by other means. 
% 
% Future work could compare the use of gamification with out leaderboards
%

>>>>

% Anuncements
At the start of each of the experiments, a call to participation was promoted through social networks
particularly on Facebook and Twitter social networks.
It is important to note that volunteers needed to log-in in to facebook and give permissions to the 
web application in order to participate, in thi case there were no anonymous volunteers. This permited the automatic access to
each participant's social network and enabled the system to store a local copy of those friends participating.
Another experiment is needed to see the effect this requirement has on participation.

@@

Before launch, each deployment was first tried with a few beta testers. When applying the leader board
gammification technique for the first time a problem was found in this stage. The problem was that some 
users were chating by giving a rating to an animation even before it was returned from the server, this was done by just
constantly clicking the mouse button. This is a common problem found in systems using leader boards because
by making the scores visible to other players they are encouraged to compete \cite{hickman2010total}. 
According to \cite{kumar2013gamification} best-practice gamification designs try to
refrain from using this element because of  problematic consequences of competition, which can result 
in negative conduct, low cooperation and collaboration, or disadvantaging certain player
demographics such as women. In order to still measure the effect of the leader board on the system, the 
problem of cheating was mitigated by disabling the rate button for a certain amount of time giving the animation
enough time to finish. But the problem persists, competitive users will try to get in to the leader board by other means.

% Chating in an IEA is a serious but common risk in volunteer based systems.  
% Future work could compare the use of gamification with out leaderboards
%
